---
title: "Toronto's unhoused population"
author: 
  - First author
thanks: "Code and data are available at: <https://github.com/SavvyUni-MT/toronto_unhouse_pop.git>."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
#### Workspace setup ####
#install.packages("here")

library(tidyverse)
library(knitr)

#### Import the data ####
toronto_shelters_clean <-
  read_csv(
    here::here("outputs/data/edited_data.csv"),
    show_col_types = FALSE
  )
```


# Introduction

You can and should cross-reference sections and sub-sections. 

The remainder of this paper is structured as follows. @sec-data....

Data is downloaded from the @opendatatoronto. We analysis the data in R (@citeR)

# Data {#sec-data}

We then create a summary statistic on the basis of monthly groups, using `summarise()` from `tidyverse` [@tidyverse]. We use `kable()` from `knitr` [@knitr] to create @tbl-toronto. 

```{r}
#| label: tbl-toronto
#| tbl-cap: Shelter usage in Toronto in 2021
#| echo: false

toronto_shelters_clean |>
  mutate(occupancy_month = month(
    occupancy_date,
    label = TRUE,
    abbr = FALSE
  )) |>
  arrange(month(occupancy_date)) |> 
  drop_na(occupied_beds) |>
  summarise(number_occupied = mean(occupied_beds),
            .by = occupancy_month) |>
  kable(
    col.names = c("Month", "Average daily number of occupied beds"),
    digits = 1
  )
```


Refer to @fig-toronto

```{r}
#| label: fig-toronto
#| fig-cap: Shelter usage in Toronto in 2021
#| echo: false

toronto_shelters_clean |>
  mutate(occupancy_month = month(
    occupancy_date,
    label = TRUE,
    abbr = FALSE
  )) |>
  arrange(month(occupancy_date)) |> 
  drop_na(occupied_beds) |>
  summarise(number_occupied = mean(occupied_beds),
            .by = occupancy_month) |>
  ggplot(aes(x=occupancy_month, y = number_occupied)) + geom_point()
```

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


